Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
some text for g1

Our final example is \texttt{g1} which is a faithful translation of
what is known as the ``awkward'' example.
\todo[inline]{insert references}

>>>>

The final example in \figurename~\ref{fig:prog-g1} consists of two
part: \texttt{g1} creates a closure with one variable $x$ in its
environment and \texttt{f4} as the code. When the closure is called,
it expects to be called with a capability for a callback and a stack
capability.

For the property we show for \texttt{g1}, the control is inverted
compared to the other examples.
